s.function

### 2024-08-19 src/oa_RF_corrected.Rmd
0595A

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE      
#   2     variance    1.221299  0.4082199  0.5829598
#   2     extratrees  1.308769  0.3297824  0.6136490
#   5     variance    1.203082  0.4241359  0.5703508
#   5     extratrees  1.280883  0.3513153  0.6124031
#   8     variance    1.214268  0.4155308  0.5674246
#   8     extratrees  1.284107  0.3502621  0.6180390
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance and
#  min.node.size = 5.

>>>>

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    3.283708  0.3202280  1.034153
#   2     extratrees  3.516978  0.2323646  1.087689
#   5     variance    3.240309  0.3354508  1.019184
#   5     extratrees  3.443571  0.2565672  1.107110
#   8     variance    3.278693  0.3251487  1.017672
#   8     extratrees  3.449965  0.2562403  1.124713
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance and min.node.size = 5.

### 2024-08-19 src/oa_RF_corrected_10.Rmd
0595A

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE      
#   2     variance    1.221299  0.4082199  0.5829598
#   2     extratrees  1.308769  0.3297824  0.6136490
#   5     variance    1.203082  0.4241359  0.5703508
#   5     extratrees  1.280883  0.3513153  0.6124031
#   8     variance    1.214268  0.4155308  0.5674246
#   8     extratrees  1.284107  0.3502621  0.6180390
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance
#  and min.node.size = 5.

>>>>

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    22.46734  0.4784290  5.681843
#   2     extratrees  24.69943  0.3875775  6.049473
#   5     variance    22.50225  0.4803563  5.664478
#   5     extratrees  23.95316  0.4143508  6.102471
#   8     variance    23.14682  0.4644807  5.678126
#   8     extratrees  24.14426  0.4095256  6.213216
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and min.node.size = 5.

### 2024-08-19 src/s_la_per_firm_corrected.Rmd
0595A

library(tidyverse)
library(broom)
library(rprojroot)
#library(rgdal)
library(sf)
library(modelr)
#library(survival)
#library(rgeos)
library(spdep)
library(tidygeocoder)
# library(geosphere)
# library(raster)
library(rms)
library(stargazer)

@@

>>>>

library(tidyverse)
library(broom)
library(rprojroot)
#library(rgdal)
library(sf)
library(modelr)
#library(survival)
#library(rgeos)
library(spdep)
library(tidygeocoder)
# library(geosphere)
# library(raster)
library(rms)
library(stargazer)
library(ggbump)

@@

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only0595_av.png")

  mutate(alpha = ifelse(abs(diff_1st) <= 3.75 | abs(diff_1st) > 253, 1, 0.5)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.5, alpha)) %>%

  mutate(q = ifelse(abs(diff_1st) <= 3.75, "05",
                    ifelse(abs(diff_1st) > 253, "95", "m"))) %>% 
  mutate(q = ifelse(is.na(diff_1st), "m", q)) %>%

  ggplot(aes(year, rank, group = ladcd, alpha=alpha)) +
  geom_bump(aes(colour = q)) + #colour = "red"
  scale_color_manual(values = c("darkorchid3", "orange", "grey70"),
                     breaks = c("05", "95"),
                     labels = c("Stability","Volatility")) + 
  labs(color = "LAD") +
  scale_y_reverse(labels = c(1, 100, 200, 300, 400)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  #theme(legend.position="none") +
  scale_x_continuous(NULL, 
                     #limits = c(1998, 2010), 
                     breaks=c(1998, 2010),
                     labels = c("1996-98","2010-12")) +
  guides(alpha = "none")

ggsave(out.path)
```
